### 2021-10-29 theoriezf/Article.tex
Add files via upload

\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{ae,lmodern}
\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

@@

\input{macros.tex}

@@

The langage of the theory IZmod uses four sorts. The first two are for
the pointed graphs and for the nodes of the pointed graphs.  In
\dedukti, we thus introduce two constants $\Graph$ and $\Node$ of type
$\Type$
\begin{verbatim}
constant symbol Graph : TYPE;
constant symbol Node : TYPE;
\end{verbatim}
As we have two sorts, we would need two universal quantifiers and two
existential quantifiers, one for each sort.  We rather use another
solution \cite{theoryU} that is to declare a constant $\Set$ of type
$\Type$ for codes of sorts, a function $\El$ of type $\Set \ra \Type$,
two constants $g$ and $n$ of sort $\Set$ and rewrite rules
$$\El~g \lra \Graph$$
$$\El~n \lra \Node$$

@@

$$eta : \Graph \ra \Node \ra \Node \ra \Prop$$
$$root : \Graph \ra \Node$$
$$cr : \Graph \ra \Node \ra \Graph$$
$$o : \Node$$
$$O : \Node$$
$$i : \Node \ra \Node$$
$$i' : \Node \ra \Node$$
$$j : \Node \ra \Node$$
$$j' : \Node \ra \Node$$
$$I : \Node \ra \Prop$$
$$J : \Node \ra \Prop$$
$$\rho : \Graph \ra \Node$$
$$\hat{\rho} : \Node \ra \Graph$$
$$Succ : \Node \ra \Node$$
$$Pred : \Node \ra \Node$$
$$Null : \Node \ra \Prop$$
$$Nat : \Node \ra \Prop$$
$$< : \Node \ra \Node \ra \Prop$$
$$simeq : \Graph \ra \Graph \ra \Prop$$
$$\in : \Graph \ra \Graph \ra \Prop$$
$$join : \Graph \ra \Graph$$
$$pair : \Graph \ra \Graph \ra \Graph$$
$$powerset : \Graph \ra \Graph$$
$$comp : \Graph \ra \El valuation \ra \El formula \ra \Graph$$
$$omega : \Graph$$
$$Cl : \Graph \ra \Graph$$

À faire en verbatim plutôt qu'en math mode, mais un pb avec certains
caractères unicode

>>>>

\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{ae,lmodern}
\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{mathtools}

@@

\input{macros.tex}
\input{lambdapi.tex}

@@

The langage of the theory IZmod uses four sorts. The first two are for
the pointed graphs and for the nodes of the pointed graphs.  In
\dedukti, we thus introduce two constants $\Graph$ and $\Node$ of type
$\Type$
\begin{lstlisting}
constant symbol Graph : TYPE;
constant symbol Node : TYPE;
\end{lstlisting}
As we have two sorts, we would need two universal quantifiers and two
existential quantifiers, one for each sort.  We rather use another
solution \cite{theoryU} that is to declare a constant $\Set$ of type
$\Type$ for codes of sorts, a function $\El$ of type $\Set \ra \Type$,
two constants $g$ and $n$ of sort $\Set$ and rewrite rules
$$\El~g \lra \Graph$$
$$\El~n \lra \Node$$

@@

\begin{lstlisting}
symbol eta : Graph → Node → Node → Prop;
symbol root : Graph → Node;
symbol cr : Graph → Node → Graph;
constant symbol o : Node;
constant symbol O : Node;
symbol i : Node → Node;
symbol i' : Node → Node;
symbol j : Node → Node;
symbol j' : Node → Node;
symbol I : Node → Prop;
symbol J : Node → Prop;
symbol ρ : Graph → Node;
symbol ρ^ : Node → Graph;
symbol Succ : Node → Node;
symbol Pred : Node → Node;
symbol Null : Node → Prop;
symbol Nat : Node → Prop;
symbol < : Node → Node → Prop;
symbol simeq : Graph → Graph → Prop;
symbol ∈ : Graph → Graph → Prop;
symbol join : Graph → Graph;
symbol pair : Graph → Graph → Graph;
symbol powerset : Graph → Graph;
symbol comp : Graph → El valuation → El formula → Graph;
symbol omega : Graph;
symbol Cl : Graph → Graph;
\end{lstlisting}
